Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-07-20 paper.tex
Added gnuplot scripts and result figures

\author{Soudabeh Barghi, Lalet Scaria, Tristan Glatard\\
  Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada\\
  {first.last}@concordia.ca\\
  $^*$ These authors have contributed equally
}

@@

@@

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
                  \caption{Complete Columns method}
                  \label{fig:Columns-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_rows_04_training}
                  \caption{Complete Rows method}
                  \label{fig:Rows-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                 \includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
                \caption{RS method}
                  \label{fig:Uniform-S-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
                  \caption{RFNU  method }
                  \label{fig:Diagonal-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
                  \caption{RFNT-L method}
                  \label{fig:triangular-L-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
                  \caption{RFNT-S method}
                  \label{fig:triangular-S-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
                  \caption{Random Unreal method}
                  \label{fig:Random-Unreal-Sample-Training-set}
        \end{subfigure}
        \caption{Sample training set for different methods with a training ratio of 0.4.}                
\end{figure}

@@

@@

We generated synthetic matrices as shown in 
Figure~\ref{fig:synthetic-data}. Each matrix has 100 files and 100 
subjects of different \emph{types}. Subjects of the same type behave 
identically and all types contain the same number of subjects $\pm$ 1 
\todo{Soudabeh: check that}. Such a decomposition by subject type 
correspond to the case where different subjects may have data of 
different nature, as it is for instance the case in the neuroimaging 
dataset of the Human Connectome Project~\cite{hcp} where not all the 
subjects have the same amount of images.

@@

We collected data to evaluate the computational reproducibility of analysis
pipelines of the Human Connectome Project~\cite{general-hcp}. We
processed a set S of 94 subjects randomly selected in the S500 HCP
release~\todo{URL} in three execution conditions with different
versions of the CentOS operating system (5.?, 6.? and 7.?), using the
PreFreesurfer, Freesurfer, PostFreesurfer and fMRIVolume pipelines
described in~\cite{hcp-pipelines} and available at \todo{URL}. For
each pipeline, we identified the set F of files produced for all
subjects in all conditions. For each condition pair and each pipeline,
we computed a binary difference matrix D of size $|F|\times|S|$, where $D_{i,j}$ is true
if file $i$ of subject $j$ was different in each condition. Rows of
$M$ are ordered by ascending file modification time in the pipeline.

Figure~\ref{fig:utility metrices} shows the difference matrices
obtained for the PreFreesurfer pipeline. The computational
reproducibility of the PreFreesurfer pipeline varies across subjects,
which motivates our study. Nevertheless, some files behave
consistently across all subjects, leading to complete black or white
lines. The ratio of positive elements in utility matrix of CentOS5 vs CentOS6(C5C6),  CentOS5 vs CentOS7(C5C7) and  CentOS6 vs CentOS7(C6C7) are
$0.34$, $0.79$ and $0.79$ respectively.

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.5\linewidth}
        \includegraphics[width=\columnwidth]{figures/utility_5vs6_PFS}
  \caption{Utility matrix of CentOS5 vs CentOS6}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
         \includegraphics[width=\columnwidth]{figures/utility_5vs7_PFS}
  \caption{Utility matrix of CentOS5 vs CentOS7}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
        \includegraphics[width=\columnwidth]{figures/utility_6vs7_PFS}
  \caption{Utility matrix of CentOS6 vs CentOS7}
  \label{fig:utility metrices}
  \end{subfigure}
\end{figure}

as it can be seen, some of the files are consistent cross the subjects 
which means that there are some cases that a file has an error in whole subjects (complete white)or 
in another case no checksum difference has been observed for a file among all subjects (complete black).
These kind of consistent behaviour makes us to discard the prediction of these file-id's elements 
from the calculated accuracy in some phases of our experiments.

% Describe your dataset: pipeline(s) used, input data, operating systems (CentOS5, 6, 7), matrix.

% 1. Prefreesurfer (what you have)
% 2. Freesurfer, with the same subjects as in Prefreesurfer.
% 3. PostFreesurfer
% 4. fmriVolume

@@

Four experiments have been conducted to evaluate the performance of our 
predictions using (1) ALS without biases, (2) ALS with biases, (3) Biases only. 
Results will be evaluated on the complete datasets and also specifically on the files that
do not behave consistently across subjects (\todo{explain this in introduction}).
\todo{the last sentence (pure accuracy) is just applied for Triangular-L, other results of ALS, ALS-biases are not applied in this case}
We evaluate prediction methods using accuracy, sensitivity and specificity defined as follows:
\[
        Accuracy = \frac{TP+TN}{TP+TN+FP+FN}
\]
\[
        Sensitivity = \frac{TP}{TP+FN}
\]
\[
        Specificity = \frac{TN}{TN+FP}
\]
Where TP is the number of True Positives (correctly predicted errors), 
FP is the number of False Positives, TN is the number of true negatives 
and FN is the number of false negatives.

We compare our methods to two references, (1) a dummy classifier that always predicts the dominant class.
as the dominant value of the utility matrix (1 or 0), (2) the Random Unreal method, used as the baseline sampling technique.

\subsection{ALS without biases}
In this phase of the experiment, the Alternating Least Squares 
technique of Collaborative Filtering is applied for all provided 
methods. Our four sampling techniques are compared in 
Figure~\ref{fig:ALS-Failure} and the results are described in the next 
sub-sections.

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-6vs7}
        \end{subfigure}
        \caption{Average accuracy of Complete Columns, RS, Complete Rows and Random Unreal methods in three different condition pairs.}
        \label{fig:ALS-Failure}
\end{figure}

\subsubsection{Random Unreal}
This method has a great performance with absolute accuracy of more than $0.95$ 
even by accessing to small training size of 10 percent. As it mentioned earlier 
this method is not applicable in pipeline due to time-stamp consideration but it 
is a good criterion to estimate the performance of other methods and try to modify 
the proposed methods in order to their accuracy be as closed as possible to the 
Random Unreal method ones.

\subsubsection{Complete Columns}
The Complete Columns method has almost a constant accuracy even if the training ratio increased and it
is almost two times less than dummy classifier in more differentiated
condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the
best case which it means in similar conditions the Complete Columns
accuracy is as much accurate as the Dummy classifier is, $0.65$
percent.
\\
\subsubsection{Complete Rows}
This method has some fluctuation over the gowth of training set size. These falactuations are more 
frequent in condition pairs which have higher difference positive ratio. 
Also by enlarging the training ratio specially between $0.3$ to $0.7$, 
we can see dummy classifier has better results than Complete Rows ones. 
In other words despite of better performance of Complete Rows than 
dummy classifier at the last 10 percent of the graph, its accuracy 
are less than dummy classifiers ones.  
\\
\subsubsection{Random Subjects-RS}
Same to the Complete Row method, RS method has some fluctuation but not as frequent 
as Complete Rows method. Although there are some up and down trends specially with 
training ratio range of $0.2$ to $0.6$ but its constant growth trend after 
training ratio $0.3$ in condition pairs with high difference positive ratio is considerable.
The method can be $0.99$ percent accurate when it has over 70 percent of the data however 
this accuracy can be achived with higher training ratio (over 80 percent) for C5C6.  
\\
\\
\noindent Figure~\ref{fig:ALS-Succeed} represents
the accuracy graph of all Random kind methods with comparison to dummy
classifier over the increment of the training ratio.\\
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-6vs7}
        \end{subfigure}
        \caption{Average performance of RFNU methods in three different condition pairs}
        \label{fig:ALS-Succeed}
\end{figure}
\subsubsection{Random File Numbers(Uniform) - RFNU}
The continuous rise of RFNU accuracy trend can be observed in Figure~\ref{fig:ALS-Succeed}.
However a 0.03 drop is recorded in C6C7 between training ratio size of $0.8$ to $0.9$. 
This method takes over the dummy accuracy after having a training size more than 40 percent 
in condition pairs of C5vsC7 and C6vsC7 but it always shows better accuracy than 
dummy classifier ($0.73$ percent with training ratio of $0.1$).\newline

% ALS-RFNT approaches
\indent As it mentioned earlier, for $\alpha < \nicefrac{1}{3}$ RFNT approaches are not applicable, 
therefor for training ratio less than $0.4$ RFNU method is employed. As a result, in terms of 
evaluating the performance of RFNT-L and RFNT-S approches, only those accuracy results are 
considered which their training set are equal or greater than 0.4 percent of the whole utility matrix.\newline

\subsubsection{RFNT-L}

In Figure~\ref{fig:ALS-Succeed}, the results show that RFNT-L performance is always more accurate than
dummy classifier even in its lowest accuracy value observed at training ratio of $0.6$ in C5C6 ($0.78$ percent).
Despite of this sudden, RFNT-L method has slight growing trend throughout the 
increment of training ratio and its accuracy is always more than $90\%$.

\subsubsection{RFNT-S}
Figure~\ref{fig:ALS-Succeed} shows the overall performance of RFNT-S methods in three different condition pairs.
Similar to RFNT-L, this method also has constant accuracy increment with maximum less accuracy of 0.07 than 
Random Unreal method throughout the experiment of C5C7 and C6C7.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{ALS with biases}
In this part of the experiment, the effect of both subject and file 
biases are considered in the prediction. Our three random sampling 
techniques (RFNU, RFNT-L and RFNT-S) are compared in 
Figure~\ref{fig:ALS-Bias-PFS} as a function of the training 
ratio $\alpha$.

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of random methods for three different condition pairs (ALS with Bias).}
        \label{fig:ALS-Bias-PFS}
\end{figure}
\todo{Add $\alpha$ to the x labels in the Figure}

All three methods reach the accuracy of the baseline Random Unreal 
method from $\alpha$=0.5. RFNT methods reach this accuracy earlier than 
RFNU, from $\alpha$=0.4. For lower training ratios, all methods 
outperform the dummy classifier for one condition pair (CentOS5 vs 
CentOS6) but this is not the case for the other conditions. It should 
be noted that, as explained before, the three methods boil down to the 
same one (RFNU) for $\alpha<$0.3.{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Bias without ALS}
In this part of our experiments we tried to eliminate the ALS prediction 
impact on the results therefore, the elements of the matrix are going to 
be predicted according to the biases of both their constitutive subject and file-id.
Figure~\ref{fig:Bias-PFS} represents
the accuracy graph of all methods as a function of the training ratio in Biases without ALS technique. 
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/Bias/Bias-5vs6-PFS}
        \end{subfigure}        
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/Bias/Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/Bias/Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of all methods for three different condition pairs (Bias without ALS).}
        \label{fig:Bias-PFS}
\end{figure}

As it can be seen, Complete Columns method is less accurate than dummy classifier
 with less than 25 percent accuracy but this is not the case for the CentOS5 vs CentOS6 
 condition pair which it outperform dummy classifier (with accuracy of 75).
Despite of inadequate accuracy of RS and Complete Rows sampling methods in ALS without Biases prediction technique,
 they surpass other methods with the same accuracy of the baseline Random Unreal method.
Triangular Distribution methods(RFNT-L, RFNT-S) reach to the baseline accuracy by $\alpha$=0.4, 
which is earlier than the same happens for RFNU  by $\alpha$>0.5.{}
In general, all methods except complete columns have high accuracy almost as accurat as the Random Unreal baseline method
in this technique of prediction.As usual, three distributional methods perform equally by the only significant 
difference at $\alpha$=0.4{}.

@@

@@

% Summary of the results and discussion. The take-home message.
%%%%%% why there is a drop in ALS-RFNT-L with 60% ratio?  
\section*{Acknowledgement}

>>>>

\author{Soudabeh Barghi, Lalet Scaria, Tristan Glatard\\
  Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada\\
  {first.last}@concordia.ca}

@@

\todo{Mention why this is Big Data}

\todo{Cite Cecile's paper}

\todo{Define reproducibility \emph{errors}}

@@

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
                  \caption{Complete Columns}
                  \label{fig:Columns-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_rows_04_training}
                  \caption{Complete Rows}
                  \label{fig:Rows-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                 \includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
                \caption{Random Subjects (RS)}
                  \label{fig:Uniform-S-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
                  \caption{RFNU}
                  \label{fig:Diagonal-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
                  \caption{RFNT-L}
                  \label{fig:triangular-L-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
                  \caption{RFNT-S}
                  \label{fig:triangular-S-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
                  \caption{Random Unreal}
                  \label{fig:Random-Unreal-Sample-Training-set}
        \end{subfigure}
        \caption{Sample training set for different methods with a training ratio of 0.4.}                
\end{figure}

@@

\todo{Soudabeh, can you remove the caption on all matrices?}

@@

We generated synthetic matrices as shown in 
Figure~\ref{fig:synthetic-data}. Each matrix has 100 files and 100 
subjects of different \emph{types}. Subjects of the same type behave 
identically and all types contain the same number of subjects $\pm$ 1 
\todo{Soudabeh: check that}. Such a decomposition by subject type 
correspond to the case where different subjects may have data of 
different nature, as it is for instance the case in the neuroimaging 
dataset of the Human Connectome Project~\cite{van2013wu} where not all the 
subjects have the same amount of images.

@@

We collected data to evaluate the computational reproducibility of analysis
pipelines of the Human Connectome Project~\cite{glasser2013minimal}. We
processed a set S of 94 subjects randomly selected in the S500 HCP
release~\todo{URL} in three execution conditions with different
versions of the CentOS operating system (5.?, 6.? and 7.?), using the
PreFreesurfer and Freesurfer pipelines
described in~\cite{glasser2013minimal} and available at \todo{URL}. For
each pipeline, we identified the set F of files produced for all
subjects in all conditions. For each condition pair and each pipeline,
we computed a binary difference matrix D of size $|F|\times|S|$, where $D_{i,j}$ is true
if file $i$ of subject $j$ was different in each condition. Rows of
$M$ are ordered by ascending file modification time in the pipeline.

Figure~\ref{fig:utility-matrices} shows the utility matrices
obtained for the PreFreesurfer and Freesufer pipeline. The computational
reproducibility of these pipelines varies across subjects,
but some files behave
consistently across all subjects, leading to complete black or white
lines.
%The ratio of positive elements in utility matrix of CentOS5 vs CentOS6(C5C6),  CentOS5 vs CentOS7(C5C7) and  CentOS6 vs CentOS7(C6C7) are
%$0.34$, $0.79$ and $0.79$ respectively.

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.45\linewidth}
        \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v6_utility_matrix.png}
  \caption{PFS, C5 vs C6}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
         \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v7_utility_matrix.png}
  \caption{PFS, C5 vs C7}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
        \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_6v7_utility_matrix.png}
  \caption{PFS, C6 vs C7}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
        \includegraphics[width=\columnwidth]{data/Utility_Matrix/FS-100files/FS-First-bound-100files.png}
  \caption{FS (first 100 files), C6 vs C7}
  \end{subfigure}
  \caption{Utility matrices, PreFreesurfer (PFS) and Freesurfer (FS) pipelines}
    \label{fig:utility-matrices}
\end{figure}

@@

Three experiments have been conducted for each dataset to evaluate the performance of our 
predictions using (1) ALS without biases, (2) ALS with biases, (3) Biases only. 
Results will be evaluated using accuracy, sensitivity and specificity defined as follows:
\[
        Accuracy = \frac{TP+TN}{TP+TN+FP+FN}
\]
\[
        Sensitivity = \frac{TP}{TP+FN}
\]
\[
        Specificity = \frac{TN}{TN+FP}
\]
Where TP is the number of True Positives (correctly predicted reproducibility errors), 
FP is the number of False Positives, TN is the number of true negatives 
and FN is the number of false negatives. \todo{Check if we want to report sensitivity and specificity, otherwise remove.}

We compare our sampling methods to (1) a dummy classifier that always predicts the value in the majority class
 and (2) the Random Unreal method, used as the baseline sampling technique.

\subsubsection{ALS without Bias}

Accuracy results for the different numbers of subject types are 
reported in Figure~\ref{fig:results-synthetic}. By construction, the 
accuracy of the dummy classifier is 0.5 for all subject types. Random 
Unreal performs very well for all subject types, which confirms that 
ALS is working correctly. Unsurprisingly, all the other methods perform 
better than the dummy classifier, and their accuracy decreases as the 
number of subject types increases.

However, only 3 methods are able to provide accuracy values above 0.85 
for all subject types: Random Subjects (RS), RFNU and RFNTL. This is 
due to the fact that these methods are the only ones that can sample 
files produced toward the end of the execution while maintaining a 
reduced number of empty columns. Surprisingly, RFNTS does not perform 
well for more than 2 subject types \todo{Check that.}.

RS, RFNU and RFNTL achieve a 90\% accuracy for a training ratio of 
about 0.85. Therefore, 15\% of the computations could potentially be 
saved in such reproducibility studies.

\begin{figure*}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-2-types.pdf}
        \caption{2 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-4-types.pdf}
        \caption{4 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-8-types.pdf}
        \caption{8 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-16-types.pdf}
        \caption{16 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-32-types.pdf}
        \caption{32 subject types}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-64-types.pdf}
        \caption{64 subject types}
\end{subfigure}
\caption{Accuracy results on synthetic data, ALS \emph{without} bias.}
\label{fig:results-synthetic}
\end{figure*}

\subsubsection{ALS with Bias}

Results of ALS with Bias are reported in Figure~\ref{fig:results-synthetic-als-bias}.
RS, RFNU and RFNTL remain the methods that best compare to Random Unreal, but the achieved
accuracy is much lower than without Biases. This is due to the fact that biases \ldots \todo{finish that.}

\begin{figure*}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-2-types.pdf}
        \caption{2 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-4-types.pdf}
        \caption{4 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-8-types.pdf}
        \caption{8 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-16-types.pdf}
        \caption{16 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-32-types.pdf}
        \caption{32 subject types}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-64-types.pdf}
        \caption{64 subject types}
\end{subfigure}
\caption{Accuracy results on synthetic data, ALS \emph{with} bias.}
\label{fig:results-synthetic-als-bias}
\end{figure*}

\subsubsection{ALS without bias}

\begin{figure*}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v6.pdf}
        \caption{PFS, CentOS5 vs CentOS6}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v7.pdf}
        \caption{PFS, CentOS5 vs CentOS7}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-6v7.pdf}
        \caption{PFS, CentOS6 vs CentOS7}
\end{subfigure}\hfill
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/FS-100files/ALS-FS100files.pdf}
        \caption{FS, CentOS6 vs CentOS7}
\end{subfigure}
\caption{Accuracy results on PreFresurfer (PFS) and Freesurfer (FS) data, ALS \emph{without} bias.}
\label{fig:results-real-als}
\end{figure*}

\subsubsection{ALS with bias}

\begin{figure*}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v6.pdf}
        \caption{PFS, CentOS5 vs CentOS6}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v7.pdf}
        \caption{PFS, CentOS5 vs CentOS7}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-6v7.pdf}
        \caption{PFS, CentOS6 vs CentOS7}
\end{subfigure}\hfill
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/FS-100files/ALS-Bias-FS100files.pdf}
        \caption{FS, CentOS6 vs CentOS7}
\end{subfigure}
\caption{Accuracy results on PreFresurfer (PFS) and Freesurfer (FS) data, ALS \emph{with} bias.}
\label{fig:results-real-als-bias}
\end{figure*}

@@

% Real values, we expect the best sampling method to remain the same.

@@

% Summary of the results and discussion. The take-home message.
%%%%%% why there is a drop in ALS-RFNT-L with 60% ratio?

\todo{Make sure the code is available and results are reproducible.}

\section*{Acknowledgement}
